\documentclass[a4paper, 10pt]{article}

\def\name    { Justin Tyler Dubs       }
\def\phone   { (919) 901-0712          }
\def\email   { jtdubs@gmail.com        }
\def\address { 5428 Berry Creek Circle \\
               Raleigh, NC 27613       }

\usepackage{resume}

\begin{document}
    \begin{resume}
        \\[2ex]
        \begin{block}
            \begin{category}{Sensus}
                \position {Senior Software Engineer} {Conservation Solutions Department}
                Sensus is the global leader in Smart Grid technologies.  The Conservation Solutions
                Department is responsible for the design-to-delivery engineering of Sensus's wireless
                water and gas meter solutions.
                \bigskip
            \end{category}
            \begin{subcategory}{Apr 10 -- Present}
                \project {FieldLogic Suite} {Lead Engineer}
                The FieldLogic Suite of applications is responsible for the field installation,
                management, and monthly reading of all metering products, wireless and otherwise.
                \\[1ex]
                FieldLogic implements Sensus's proprietary, encrypted network protocol to allow running
                on a performance- and memory-constrained platform while allowing transmissions with a
                timing precision of 0.1ms.
                \\[1ex]
                Responsibilities: \\
                -- Designed and lead implementation of a complete software stack that is used by thousdands of utility companies. \\
                -- Lead a geographically distributed team of software developers and testers. \\
                -- Developed software schedules and planned releases with project management organization. \\
                -- Reviewed test plans and tracked test progress. \\
                -- Gathered customer requirements from, and reviewed software concepts with, marketing, sales and support organizations. \\
                -- Planned and helped organize manuals and training materials with documentation and training organizations. \\
                \\[1ex]
                Principal technologies: \emph{C\#, SQLite, WPF, WinForms, Windows XP/7/8, Windows Mobile 6.5}.
                \bigskip
            \end{subcategory}
            \begin{subcategory}{Jun 13 -- Present}
                \project {FieldLogic API} {Lead Engineer}
                The FieldLogic API is designed to allow third-party work order management systems
                to the utilize FieldLogic Suite's capabilities and perform automated installations
                of Sensus's metering products.
                \\[1ex]
                Responsibilities: \\
                -- Gather requirements from work order management companies. \\
                -- Create a development plan and schedule for fulfillment of gathered requirements. \\
                -- Design and document a communications protocol to meet their requirements. \\
                -- Architect and oversee implementation of communications protocol. \\
                -- Collaborate with work order management companies to aide comprehension,
                answer technical questions, and guide integration with the API. \\
                \\[1ex]
                Principal technologies: \emph{C\#, Windows Mobile 6.5}.
                \bigskip
            \end{subcategory}
        \end{block}
        \begin{block}
            \begin{category}{Lenovo}
                \position {Research Engineer} {Raleigh Advanced Technolgoy Center}
                -- Lenovo Master Inventor with over 30 filed patents and 20 technical publications. \\
                -- 2009-10 Inventor of the Year. \\
                \par
                Job responsibilities: \\
                -- Design, prototype and deliver proof--of--concept implementations of new product concepts. \\
                -- Meet with external technology providers to evaluate solutions for portfolio inclusion. \\
                -- Protect our current and future product portfolios with substantial IP.
                \bigskip
            \end{category}
            \begin{subcategory}{Jan 09 -- Apr 10}
                \project {Lenovo Skylight} {Software Architect and Lead Developer}
                Lenovo Skylight marked Lenovo's entry into the emerging Smartbook market.
                It was an ARM/Linux notebook with a custom software stack that focuses
                on multimedia consumption and internet connectivity.
                Skylight was to launch in July of 2010.
                \\[1ex]
                Responsibilities: \\
                -- Designed and prototyped the multimedia and content indexing systems. \\
                -- Designed an API to allow external applications to access the indexed metadata. \\
                -- Designed an API to allow external applications to control multimedia playback. \\
                -- Lead a small team of developers to complete development of these systems and APIs. \\
                -- Lead a three week workshop in Beijing, China to transfer ownership of these components from research to development.
                \\[1ex]
                Principal technologies: \emph{Python, GTK, GStreamer, D-Bus}.
                \bigskip
            \end{subcategory}
            \begin{subcategory}{Feb 07 -- Nov 08}
                \project {Lenovo Constant Connect} {Software Architect and Developer}
                Lenovo Constant Connect is a Large Enterprise market offering that enables
                seamless mail flow to and from your PC by using your Blackberry as a mail
                gateway.  Mail can be cached on the always-powered Constant Connect card for
                transfer between the PC and Blackberry when they next find themselves within
                bluetooth range, even if the PC is asleep or off.
                \\[1ex]
                This distributed system consists of a set of Windows services, an Express Card
                form-factor embedded computer, and a set of Blackberry services.
                \\[1ex]
                Responsibilities: \\
                -- Design and implementation of the communication and data synchronization frameworks. \\
                -- Design and implementation of all value-add software for the embedded system. \\
                -- Design and implementation of PC system services.
                -- Co-design and implementation of hardware control logic for embedded system.
                \\[1ex]
                Principal technologies: \emph{C\#, .NET, .NET CF, Win CE 5.0}.
                \bigskip
            \end{subcategory}
            \begin{subcategory}{Jun 05 -- Nov 06}
                \project {Lenovo TechBuddy} {Software Developer}
                Lenovo TechBuddy is an online services platform.  Customers can purchase
                a varienty of services, from system configuration assistance to general
                troubleshooting.  Customer Service Representatives then accept requests,
                chat with the customer, access the system's configuration history and even
                perform remote system takeover.
                \\[1ex]
                Responsibilities: \\
                -- Mock--up various HelpDesk concepts to elicit feedback from Marketing and Product Development. \\
                -- Develop prototype of Customer Service Rep application.
                % -- Develop and maintain Use Case document describing CSR functionality.
                \\[1ex]
                Principal technologies: \emph{C++, Qt}.
                \bigskip
                \bigskip
            \end{subcategory}
        \end{block}
        \begin{block}
            \begin{category}{IBM}
                \position {Software Engineer} {Technology Strategy, Personal Computer Division}
                \smallskip
            \end{category}
            \begin{subcategory}{Mar 04 -- Apr 05}
                \project {Secure Internet Gateway Appliance} {Software Developer}
                SIGA is a small-business PC management server, run on commodity desktop
                hardware, which would provide software inventorying, shared storage,
                configuration distribution and remote command execute.
                \\[1ex]
                Responsibilities: \\
                -- Design and implement the field-update system for the management server. \\
                -- Implement client GUI to allow end--users to make use of managed services. \\
                -- Traveled to New York to setup and support customers during our Beta program.
                \\[1ex]
                Principal technologies: \emph{C++, Qt, Debian}.
                \bigskip
                \bigskip
            \end{subcategory}
        \end{block}
        \begin{block}
            \begin{category}{IBM}
                \position {Technical Intern} {Software Group}
                \smallskip
            \end{category}
            \begin{subcategory}{Sep 03 -- Dec 03}
                \project {IBM Extreme Blue} {Software Developer}
                This internship program pairs interns with full--time development and
                business staff members.  A seed idea is fleshed--out into a simple
                product concept, and the concept is prototyped.
                \\[1ex]
                We created a small--business, PC preloading system.  Its web front-end allowed
                mapping of employees to corporate functions to preload images.  The PCs would
                then network boot, find the right image, and install themselves.
                \\[1ex]
                Responsibilities: \\
                -- Design the implement the configuration database. \\
                -- Modify IBM Image Ultra Builder to be driven entirely from the command-line. \\
                -- Write boot code to identify the machine, and therefore OS image, and install it.
                \bigskip
            \end{subcategory}
            \begin{subcategory}{Jan 02 -- Aug 02}
                \project {WebSphere Studio} {Software Tester}
                IBM's WebSphere product suite is an enterprise, software--devlopment solution.  Among
                its many features, is the ability to deploy code to and debug code on IBM z/OS systems.
                \\[1ex]
                Responsibilities: \\
                -- Develop test cases for WebSphere's z/OS components. \\
                -- Execute test cases and report bugs. \\
                -- Participate in frequent call with development to discuss and clarify bug status.
                \bigskip
                \bigskip
            \end{subcategory}
        \end{block}
        %\begin{block}
        %    \begin{category}{planetibiz.com}
        %        \position {Contract Developer}  {}
        %        \smallskip
        %    \end{category}
        %    \begin{subcategory}{Jan 03 -- May 03}
        %        \project {Newsletter Distribution System} {Contract Developer}
        %        I was hired to created a simple, web--based, newsletter distribution system.
        %        It held a set of customer records and a collection of newsletter templates,
        %        and had a mechanism for applying a template to a set of customer records and
        %        delivering the resulting emails in parallel through a collection of SMTP servers.
        %        \\[1ex]
        %        Responsibilties: \\
        %        -- Design, develop and deliver a reliable solution within the alloted timeframe.
        %        \\[1ex]
        %        Principal technologies: \emph{Perl, PHP, HTML}.
        %        \bigskip
        %        \bigskip
        %    \end{subcategory}
        %\end{block}
        \begin{block}
            \begin{category}{Education}
                \degree {B.S. of Computer Science} {North Carolina State University}
                        { }                        {Fall 1999 - Spring 2004}
            \end{category}
        \end{block}
    \end{resume}
\end{document}
